---
title: "p8105_hw1_vc2692"
author: Vaidehi Chudgar
date: "09-20-2025"
output: 
  github_document:
---

```{r - loading tidyverse}
library(tidyverse)

```

# Problem 1

## Loading dataset

I first downloaded a package containing the dataset by running code 'install.packages("moderndive")' directly in the console.

Below, I load the moderndive library and load the early_january_weather dataset.

```{r - loading dataset}
library(moderndive)
data("early_january_weather")
```

## Summarizing dataset

Next, I skim data for summary of dataset.

```{r - skim data}
skimr::skim(early_january_weather)
```

* The early_january_weather dataset provides hourly meteorological data for LGA, JFK, and EWR for the first half of January 2013. There are 15 variables in this dataset. Names of important variables include:
    * Origin - weather station
    * year, month, day, hour - information on time of recording
    * temp, dewp - temperature and dewpoint in F
    * humid - Relative humidity
    * wind_dir, wind_speed, wind_gust - Wind direction (in degrees)
    * precip - Precipitation, in inches 
    * pressure - Sea level pressure in millibars
    * visib - Visibility in miles
    * time_hour - Date and hour of the recording as a POSIXct date.
    
* There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

* The mean temperature is `r mean(early_january_weather$temp)`.

## Scatter Plot

The following is code for the scatter plot.


```{r - scatterplot}
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

The scatter plot shows a 24 hour cycle for temperature as shown by the zig zag pattern of the graph. Generally, we see that as the days progress into mid-January, the average temperature  and humidity increases. 


# Problem 2

## Creating dataframe

First I am creating my dataframe.

```{r - Creating dataframe}
set.seed(1234)

problem2_df = tibble(
  numeric_vector = rnorm(n=10),
  logical_vector = numeric_vector > 0,
  character_vector = c("blue", "red", "yellow", "green", "purple", "black", "gray", "beige", "indigo", "violet"),
  factor_vector = factor(c("low", "medium", "high", "low", "medium", "high","low", "medium", "high", "low"))
)
```

## Calculating means

Taking the mean of each of the variables.

```{r - mean calculations}
mean(pull(problem2_df, numeric_vector))
mean(pull(problem2_df, logical_vector))
mean(pull(problem2_df, character_vector))
mean(pull(problem2_df, factor_vector))

```

I am only able to take the mean of the norm_samp vector and logical_vector.

I get NA if I try to take the mean of the character_vector and factor_vector.


## Converting to numeric variables

Below, I convert variables to numeric variables.

```{r - convert to numeric, echo=TRUE, results='hide', warning=FALSE, message=FALSE}

problem2_df |> 
mutate(across(c(logical_vector, character_vector, factor_vector), as.numeric))

```

When I try to apply the as.numeric function to the logical, character, and factor variable, I am not able to convert the character_vector. This explains why NA is returned when I try to take the mean of character_vector, as there are no numbers underlying this vector that R can use to take the mean of this vector. 

I am able to convert the factor_vector to a numeric variable, but since I did not do this before taking the mean, R was not able to provide a mean for the factor_vector variable in the previous step.








