---
title: "p8105_hw1_vc2692"
output: github_document
author: Vaidehi Chudgar
date: "2025-09-17"
---

```{r - loading tidyverse}
library(tidyverse)

```

## Problem 1

I first downloaded a package containing the penguins dataset by running code directly in the console.

Next, I am loading the moderndive library and loading the early_january_weather dataset

```{r - loading dataset}
library(moderndive)
data("early_january_weather")
```

Next, I skim data for summary of dataset

```{r - skim data}
skimr::skim(early_january_weather)
```

* There are 15 variables in this dataset. Names of important variables include temp, dep, humid, wind_dir, wind_Speed, wind_gust, precip, pressure, visib. 
* There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.
* The mean temperature is `r mean(early_january_weather$temp)`.

### Plot

The following is code for the scatter plot.


```{r - scatterplot}
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

The scatter plot shows a 24 hour cycle for temperature as shown by the zig zag pattern of the graph. Generally, we see that as the days progress into mid-January, the average temperature  and humidity increases. 


